The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
switch fig 1 to include_graphics

\captionsetup[figure]{labelformat=empty}

![**Figure 1**](../graphics/figure1.png)

**Figure 1**: Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.
\clearpage

>>>>

<!-- \captionsetup[figure]{labelformat=empty} -->

(ref:spacetime) Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.

```{r spacetime, fig.cap='(ref:spacetime)'}
knitr::include_graphics('../graphics/figure1.png')
```
